Circumpolar variations in Southern Ocean eddy dynamics:\\An ensemble approach

### 2021-06-06 paper/main.tex
starting intro

\documentclass{agujournal2019-navid}

@@

% \linenumbers

@@

% \journalname{Geophysical Research Letters}

\usepackage{scalerel, stackengine}
\setstackEOL{\#}
\stackMath
\def\hatgap{2pt}
\def\subdown{-2pt}
\newcommand\reallywidehat[2][]{ \renewcommand\stackalignment{l} \stackon[\hatgap]{#2}{ \stretchto{
    \scalerel*[\widthof{$#2$}]{\kern-.6pt\bigwedge\kern-.6pt}
    {\rule[-\textheight/2]{1ex}{\textheight}}}
    {0.5ex}_{\smash{ \belowbaseline[\subdown]{\scriptstyle#1} }}
}}

%% MACROS

% Vector calculus 
  \newcommand{\p}		{\partial}
  \newcommand{\bnabla}	{\boldsymbol \nabla}
  \newcommand{\grad}	{\bnabla}
\renewcommand{\div}	    {\bnabla \bcdot}
  \newcommand{\bcdot}	{\boldsymbol \cdot}
  \newcommand{\lap}		{\triangle}

% Boldsymbols
\newcommand{\bu}		{\boldsymbol{u}}
\newcommand{\bx}		{\mathbfit x}
\newcommand{\bU}		{\mathbfit{U}}
\newcommand{\bX}		{\mathbfit{X}}
\newcommand{\bxh}		{\hspace{0.1em} \boldsymbol{\hat x}}
\newcommand{\byh}		{\hspace{0.1em}\boldsymbol{\hat y}}
\newcommand{\bzh}		{\hspace{0.1em}\boldsymbol{\hat z}}
\newcommand{\bnh}		{\hspace{0.1em}\boldsymbol{\hat n}}
\newcommand{\bxi}		{\ensuremath {\boldsymbol {\xi}}}

% Greek
\newcommand{\ep}		{\epsilon}
\newcommand{\om}		{\omega}
\newcommand{\kap}		{\kappa}
\newcommand{\sig}		{\sigma}
\newcommand{\gam}	  {\gamma}
\newcommand{\lam}		{\lambda}

% Romans
\newcommand{\ee}		{\mathrm{e}}
\newcommand{\ii}		{\mathrm{i}}
\newcommand{\dd}		{{\rm d}}
\newcommand{\id}		{{\, \rm d}}

% Misc
\newcommand{\Dt}[1]	    {\mathrm{D}_t #1}
\newcommand{\half}		{\tfrac{1}{2}}
\newcommand{\where}	    {\qquad \text{where} \qquad}
\newcommand{\andand}	{\qquad \text{and} \qquad}
\newcommand{\com}		{\, ,}
\newcommand{\per}		{\, .}
\newcommand{\defn}	    {\ensuremath{\stackrel{\mathrm{def}}{=}}}
\renewcommand{\equiv} {\ensuremath{\stackrel{\mathrm{def}}{=}}}
\newcommand{\av}[1]	    {\left \langle {#1} \right \rangle}
\newcommand{\beq}		{\begin{equation}}
\newcommand{\eeq}		{\end{equation}}
\newcommand{\Pa}		{\mathrm{N}\,\mathrm{m}^{-2}}
\newcommand{\rhom} {\rho_{\mathrm{m}}}
\newcommand{\ws} {\mathrm{WS}}
\newcommand{\tfs} {\mathrm{TFS}}
\newcommand{\ifs} {\mathrm{IFS}}
\newcommand{\bd} {\mathrm{BD}}
\newcommand{\hb} {h_{\mathrm{bot}}}
\newcommand{\pb} {p_{\mathrm{bot}}}

\hypersetup{
	breaklinks,
	colorlinks=true,
	linkcolor=Blue,
  urlcolor=Purple,
	citecolor=Purple,
%	allcolors=black,
	pdfauthor={N. C. Constantinou and A. McC. Hogg}
 }

@@

Model description (Thierry)

OCCIPUT strategy (Thierry)

@@

In the South Atlantic Ocean (orange box in Fig.~\ref{Fig:3}a) the system is more dominated by intrinsic variance ($R_i=0.65$) and is poorly correlated with wind stress forcing (Fig.~\ref{Fig:3}c,e), reinforcing the circumpolar variability of the EKE response to wind.
Other regions (not shown) highlight different aspects of the response, with almost no correlation with wind forcing over the Southeast Pacific Ocean, and a long, $\sim30$-month response in the Southwest Indian Ocean with strong intrinsic variability.
The circumpolar variation in both EKE response times and intrinsic variability suggests that the two-timescale response seen in Fig. \ref{Fig:2} may be created by different processes, which each dominate in different regions of the Southern Ocean.

@@

\bibliography{basic_references}

>>>>

\documentclass{agujournal2019}

@@

\usepackage{natbib}

\linenumbers

@@

\journalname{JGR: Oceans}

@@

\subsection{The OCCIPUT ensemble}

The methodology employed in this study is derived from the probabilistic approach to ocean modelling outinlined by \citet{Bessieres2017}.
We use output from the OCCIPUT (oceanic chaos – impacts, structure, predictability) ensemble of 50 eddy-permitting ocean model simulations, run in lock-step \citep{Leroux2018}.
This ensemble is based on the DRAKKAR-ORCA025 \citep[e.g.][]{Barnier2006} implementation of the NEMO modelling system \citep{Madec2012}.
The ensemble incorporates ocean-sea ice hindcast simulations for the period 1960-2015.
The ensemble uses the DRAKKAR Forcing Set DFS5.2 (Dussin 2016) with  0.25$^\circ$ lateral resolution and 75 vertical levels.

@@

In the South Atlantic Ocean (orange box in Fig.~\ref{Fig:3}a) the system is more dominated by intrinsic variance ($R_i=0.65$) and is poorly correlated with wind stress forcing (Fig.~\ref{Fig:3}c,e), reinforcing the circumpolar variability of the EKE response to wind.
Other regions (see Fig. \ref{Fig:4}) highlight different aspects of the response;  with almost no correlation with wind forcing over the Southwest Indian Ocean (the Agulhas meander region; Fig. \ref{Fig:4}b) or the Central South Pacific (Fig. \ref{Fig:4}d).
In both of these regions, intrinsic variability dominates the signal.
On the other hand, the Southeast Pacific (north of the main pathway of the ACC) shows a strong and coherent multi-year response to wind stress; albeit with a very weak EKE signal (one tenth the magnitude of the core of the ACC).
The circumpolar variation in both EKE response times and intrinsic variability suggests that the two-timescale response seen in Fig. \ref{Fig:2} may be created by different processes, which each dominate in different regions of the Southern Ocean.

\begin{figure}[t]
\begin{center}
\includegraphics[width=\hsize]{Figure4}
\caption{Eddy kinetic energy statistics within sub-regions of the Southern Ocean. (a) Map showing Ensemble Mean EKE, along with 3 boxes over which a regional EKE analysis is applied; (b) Regional analysis of the Southwest Indian Ocean showing ensemble mean EKE in cyan, individual ensemble members EKE in grey and local wind stress averaged over the region in black; (c) Lagged correlation of ensemble mean EKE in each of the three regions; (d) Regional analysis of the South CentralPacific Ocean showing ensemble mean EKE in red, individual ensemble members EKE in grey and local wind stress averaged over the region in black; and (3) Regional analysis of the Southeast Pacific Ocean showing ensemble mean EKE in orange, individual ensemble members EKE in grey and local wind stress averaged over the region in black. The fraction of intrinsic variance in each region is shown in the caption of panels (b), (d) and (e).}
\label{Fig:4}
\end{center}
\end{figure}

@@

\bibliography{references}
